Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-07-20 AM+draft.tex
12/07/18 working on discussion v1

Eagle is a new method and R package for multiple locus association mapping. It differs from other multiple locus methods. It can handle large datasets due to dimension reduction It treats association mapping as a model selection instead of a variable selection problem so we don?t have to deal with multiple testing issues. Its results are immediately interpretable. As we saw in the simulation study, Eagle has considerably higher power than single-locus methods and is comparable in run time. However, It was in the analysis of the mouse data that the true worth of Eagle is evident. With Eagle, we found more than double the results than with single locus association mapping, the method of choice and these extra results were all validated as true.

>>>>

Eagle is a new method (and R package) for multiple-locus association mapping. It differs from other multiple-locus methods. Its results are 
immediately interpretable,  it can handle much larger datasets due to dimension reduction, and it treats association mapping as a model selection instead of a variable selection problem which avoids multiple testing issues. As we saw in the simulation study, Eagle has considerably higher power than single-locus methods and is comparable in run time. However, the true worth of Eagle is apparent from the analyses of the mouse data. It  found 
more than double the SNP-trait associations than with single-locus association mapping, the method of choice. Furthermore, these extra results 
were not false positives but true verifiable results.  Eagle was built to make multiple-locus association mapping an attractive alternative 
to single-locus association mapping.

High-throughput array-based technologies 
continue to drive down the cost of collecting SNP data. Also, access to whole-genome sequence is no longer a distant reality. The cost is still 
prohibitive for large scale deployment but this will change. 
The datasets being generated in GWASs are only going to increase in size over the coming years. 
This is why we have structured the Eagle package for continued development. We are already experimenting with a GPU-based version of Eagle. 
Early results suggest that for small to moderate sized datasets (<10,000 samples), there is little improvement in performance over CPU-based 
computation.  However, for larger study sizes, we are seeing up to a 40\% decrease in run times which is encouraging for prototype code. 
We also have plans for Eagle to run on computer clusters. Structuring Eagle for larger-than-memory calculations was a 
preemptive step on our part in this direction.

In our simulation study, we compared the performance of Eagle against six multiple-locus methods.  We found that Eagle outperforms these methods. 
However, we are cognisant that our deductions are contingent on several implementation choices. We chose to calculate the significance of the 
SNP effects from bigRR, LMM-Lasso, and glmnet via stability selection.  Permutation (ref) and multi sample-splitting (ref) are also equally valid empirical approaches. Stability selection though has the advantage of being based on repeated sampling of only a proportion (50\% in our case) of the 
data. Also, when analysing the (sub)samples, calculating a regularisation method's entire solution path is avoided.  Instead,  analyses are 
performed for a fixed value of the regularisation parameter, greatly reducing the amount of computation.
